---
title: "Concentration of molecules by class across the gradient in urban cover"
author: "Rodolfo Pelinson"
date: "2024-11-13"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r,  echo= FALSE, eval = TRUE, warning=FALSE, message=FALSE, include=FALSE}
library(vegan)
library(shape)
library(scales)
library(metacom)
library(AICcmodavg)
library(bbmle)

data_farmacos <- read.csv("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/data/antidepressivos_r.csv")
data_farmacos <- data_farmacos[,which(colnames(data_farmacos)!="Norfluoxetina")]
data_general <- read.csv("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/data/planilha_master_r.csv")

data_farmacos_reference <- data_farmacos[1,]
data_farmacos_class <- data_farmacos[2,]
data_farmacos <- data_farmacos[-c(1,2),]

data_farmacos$urb <- data_general$urb[match(data_farmacos$bacia,data_general$microbacia)]

data.frame(data_farmacos$bacia, data_farmacos$urb, data_farmacos$Decil)

data_farmacos$urb[data_farmacos$bacia == "ebb08" | 
                    data_farmacos$bacia == "ebb09" |
                    data_farmacos$bacia == "ebb11" |
                    data_farmacos$bacia == "ebb12"] <- 0 


data_farmacos$urb[is.na(data_farmacos$urb)] <- data_farmacos$Decil[is.na(data_farmacos$urb)] + 5

urb <- data_farmacos$urb
Decil <- data_farmacos$Decil
bacia <- data_farmacos$bacia

data_farmacos <- data_farmacos[,-c(1,2,ncol(data_farmacos))]
data_farmacos_reference <- data_farmacos_reference[,-c(1,2)]
data_farmacos_class <- data_farmacos_class[,-c(1,2)]

data_farmacos <- data.frame(lapply(data_farmacos,as.numeric))

data_farmacos_reference <- data_farmacos_reference[,colSums(data_farmacos)>0]
data_farmacos_class <- data_farmacos_class[,colSums(data_farmacos) > 0]
data_farmacos <- data_farmacos[,colSums(data_farmacos) > 0]


data_farmacos_class <- unlist(c(data_farmacos_class))
data_farmacos_reference <- unlist(c(data_farmacos_reference))

classess <- unique(data_farmacos_class)

data_farmacos_by_class <- list()

for(i in 1:length(classess)){
  sums <- rowSums(data_farmacos[,data_farmacos_class == classess[i]]) 
  data_farmacos_by_class[[i]] <- sums
  names(data_farmacos_by_class)[i] <- classess[i]
}

data_farmacos_by_class <- data.frame(bacia, Decil, urb, data_farmacos_by_class)

data_farmacos_class

LQ <- tapply(data_farmacos_reference, INDEX = data_farmacos_class, unique)


weights <- rep(1,length(data_farmacos_by_class$urb))
weights[data_farmacos_by_class$urb == 0] <- 1

data_farmacos_by_class$all <- data_farmacos_by_class$SNRI +
  data_farmacos_by_class$Aminoketone + 
  data_farmacos_by_class$SSRI+ 
  data_farmacos_by_class$Tricyclic


```


```{r, message=FALSE, warning=FALSE}
library(vegan)
library(shape)
library(scales)
library(AICcmodavg)
library(bbmle)
library(mgcv)
library(DHARMa)
```


Here we use a custom function that I made to fit several gam models with different maximum numbers of k and than make model selection using AICc. This function uses the gam function from mgcv package.

```{r, fig.width=10, fig.align= "center", message = FALSE}
source("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/scripts/functions/select_gam.R")

all_model <- select_gam(y = data_farmacos_by_class$all, x = data_farmacos_by_class$urb, drop.intercept = FALSE, family = "tw")
par(mfrow = c(1,2))
plotQQunif(simulateResiduals(all_model$best_model), testUniformity = FALSE, testOutliers = FALSE, testDispersion = FALSE)
plotResiduals(simulateResiduals(all_model$best_model), quantreg = FALSE, smoothScatter = FALSE, absoluteDeviation = FALSE)
all_model$AICTAB

SNRI_model <- select_gam(y = data_farmacos_by_class$SNRI, x = data_farmacos_by_class$urb, drop.intercept = FALSE, family = "tw")
plotQQunif(simulateResiduals(SNRI_model$best_model), testUniformity = FALSE, testOutliers = FALSE, testDispersion = FALSE)
plotResiduals(simulateResiduals(SNRI_model$best_model), quantreg = FALSE, smoothScatter = FALSE, absoluteDeviation = FALSE)
SNRI_model$AICTAB

SSRI_model <- select_gam(y = data_farmacos_by_class$SSRI, x = data_farmacos_by_class$urb, drop.intercept = FALSE, family = "tw")
plotQQunif(simulateResiduals(SSRI_model$best_model), testUniformity = FALSE, testOutliers = FALSE, testDispersion = FALSE)
plotResiduals(simulateResiduals(SSRI_model$best_model), quantreg = FALSE, smoothScatter = FALSE, absoluteDeviation = FALSE)
SSRI_model$AICTAB

Aminoketone_model <- select_gam(y = data_farmacos_by_class$Aminoketone, x = data_farmacos_by_class$urb, drop.intercept = FALSE, family = "tw")
plotQQunif(simulateResiduals(Aminoketone_model$best_model), testUniformity = FALSE, testOutliers = FALSE, testDispersion = FALSE)
plotResiduals(simulateResiduals(Aminoketone_model$best_model), quantreg = FALSE, smoothScatter = FALSE, absoluteDeviation = FALSE)
Aminoketone_model$AICTAB

Tricyclic_model <- select_gam(y = data_farmacos_by_class$Tricyclic, x = data_farmacos_by_class$urb, drop.intercept = FALSE, family = "tw")
plotQQunif(simulateResiduals(Tricyclic_model$best_model), testUniformity = FALSE, testOutliers = FALSE, testDispersion = FALSE)
plotResiduals(simulateResiduals(Tricyclic_model$best_model), quantreg = FALSE, smoothScatter = FALSE, absoluteDeviation = FALSE)
Tricyclic_model$AICTAB

```

Our models generally fitted well within the chosen statistical distribution (tweedie). Residuals sometimes exhibited somewhat lower values for low fitted values for the total concentration of antidepressants, which might indicate that there might be other important predictors to the number of antidepressants found in streamwater. Still, all models including urban cover as a predictor was considered by far more plausible than the model without any effect of urban cover. 

\ 
\ 

Ploting the best models:

```{r, fig.asp=1.3, fig.width=8, fig.align= "center", dev.args=list(pointsize = 15)}
ylab.cex <- 0.9
xlab.cex <- 0.9
axis.cex <- 0.75
line_labs <- 1.25
line_axis <- -0.75
tck <- -0.03
cex.points <- 0.7
line_lwd <- 1.25
cex.letter <- 1.25
x_letter = 2
y_letter = 98



all_plot <- function(letter = "",  x_letter = 0, y_letter = 100 ){
  plot(data_farmacos_by_class$all ~ data_farmacos_by_class$urb , type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "")
  title(xlab = "Urban cover (%)", line = line_labs, cex.lab = xlab.cex)
  title(ylab = "Total antidepressant", line = 2, cex.lab = ylab.cex)
  title(ylab = "concentration (ng/L)", line = 1.25, cex.lab = ylab.cex)

  polygon(y = c(all_model$estimates_best$lwr, all_model$estimates_best$upr[101:1]),
          x = c(0:100,100:0), col = "grey90", border = FALSE)
  abline(h = LQ$all, lty = 2, col = "brown")
  axis(1, tick = TRUE, line = 0, labels = FALSE,  tck = tck); axis(1, tick = FALSE, cex.axis = 0.7, line = line_axis, gap.axis = -10)
  axis(2, tick = TRUE, line = 0, labels = FALSE,  tck = tck); axis(2, tick = FALSE, cex.axis = 0.7, line = line_axis, gap.axis = -10)
  lines(c(0:100), all_model$estimates_best$fit, lty = 1, lwd  = line_lwd)
  points(x = data_farmacos_by_class$urb, y = data_farmacos_by_class$all, pch = 16, cex = cex.points)
  box()
  margins <- par()$mar
  par(new = TRUE, mar = c(0,0,0,0))
  plot(NA , type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "", bty = "n", xlim = c(0,100), ylim = c(0,100))
  text(x = x_letter, y = y_letter, labels = letter, font = 2, cex = 1.5, adj = 0)
  par(mar = margins)
}


SNRI_plot <- function(letter = ""){
  plot(data_farmacos_by_class$SNRI ~ data_farmacos_by_class$urb , type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "")
  title(xlab = "Urban cover (%)", line = line_labs, cex.lab = xlab.cex)
  title(ylab = "SNRI (ng/L)", line = line_labs, cex.lab = ylab.cex)
  
  polygon(y = c(SNRI_model$estimates_best$lwr, SNRI_model$estimates_best$upr[101:1]),
          x = c(0:100,100:0), col = "grey90", border = FALSE)
  abline(h = LQ$SNRI, lty = 2, col = "brown")
  axis(1, tick = TRUE, line = 0, labels = FALSE,  tck = tck); axis(1, tick = FALSE, cex.axis = axis.cex, line = line_axis, gap.axis = -10)
  axis(2, tick = TRUE, line = 0, labels = FALSE,  tck = tck); axis(2, tick = FALSE, cex.axis = axis.cex, line = line_axis, gap.axis = -10)
  lines(c(0:100), SNRI_model$estimates_best$fit, lty = 1, lwd  = line_lwd)
  points(x = data_farmacos_by_class$urb, y = data_farmacos_by_class$SNRI, pch = 16, cex = cex.points)
  box()
  margins <- par()$mar
  par(new = TRUE, mar = c(0,0,0,0))
  plot(NA , type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "", bty = "n", xlim = c(0,100), ylim = c(0,100))
  text(x = x_letter, y = y_letter, labels = letter, font = 2, cex = 1.5, adj = 0)
  par(mar = margins)
}


SSRI_plot <- function(letter = ""){
  plot(data_farmacos_by_class$SSRI ~ data_farmacos_by_class$urb , type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "")
  title(xlab = "Urban cover (%)", line = line_labs, cex.lab = xlab.cex)
  title(ylab = "SSRI (ng/L)", line = line_labs, cex.lab = ylab.cex)
  
  polygon(y = c(SSRI_model$estimates_best$lwr, SSRI_model$estimates_best$upr[101:1]),
          x = c(0:100,100:0), col = "grey90", border = FALSE)
  abline(h = LQ$SSRI, lty = 2, col = "brown")
  axis(1, tick = TRUE, line = 0, labels = FALSE,  tck = tck); axis(1, tick = FALSE, cex.axis = axis.cex, line = line_axis, gap.axis = -10)
  axis(2, tick = TRUE, line = 0, labels = FALSE,  tck = tck); axis(2, tick = FALSE, cex.axis = axis.cex, line = line_axis, gap.axis = -10)
  lines(c(0:100), SSRI_model$estimates_best$fit, lty = 1, lwd  = line_lwd)
  points(x = data_farmacos_by_class$urb, y = data_farmacos_by_class$SSRI, pch = 16, cex = cex.points)
  box()
  margins <- par()$mar
  par(new = TRUE, mar = c(0,0,0,0))
  plot(NA , type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "", bty = "n", xlim = c(0,100), ylim = c(0,100))
  text(x = x_letter, y = y_letter, labels = letter, font = 2, cex = 1.5, adj = 0)
  par(mar = margins)
  
}


Aminoketone_plot <- function(letter = ""){
  plot(data_farmacos_by_class$Aminoketone ~ data_farmacos_by_class$urb , type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "")
  title(xlab = "Urban cover (%)", line = line_labs, cex.lab = xlab.cex)
  title(ylab = "Aminoketone (ng/L)", line = line_labs, cex.lab = ylab.cex)
  
  polygon(y = c(Aminoketone_model$estimates_second$lwr, Aminoketone_model$estimates_second$upr[101:1]),
          x = c(0:100,100:0), col = "grey90", border = FALSE)
  abline(h = LQ$Aminoketone, lty = 2, col = "brown")
  axis(1, tick = TRUE, line = 0, labels = FALSE,  tck = tck); axis(1, tick = FALSE, cex.axis = axis.cex, line = line_axis, gap.axis = -10)
  axis(2, tick = TRUE, line = 0, labels = FALSE,  tck = tck); axis(2, tick = FALSE, cex.axis = axis.cex, line = line_axis, gap.axis = -10)
  lines(c(0:100), Aminoketone_model$estimates_best$fit, lty = 1, lwd  = line_lwd)
  points(x = data_farmacos_by_class$urb, y = data_farmacos_by_class$Aminoketone, pch = 16, cex = cex.points)
  box()
  margins <- par()$mar
  par(new = TRUE, mar = c(0,0,0,0))
  plot(NA , type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "", bty = "n", xlim = c(0,100), ylim = c(0,100))
  text(x = x_letter, y = y_letter, labels = letter, font = 2, cex = 1.5, adj = 0)
  par(mar = margins)
  
}



Tricyclic_plot <- function(letter = ""){
  plot(data_farmacos_by_class$Tricyclic ~ data_farmacos_by_class$urb , type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "")
  title(xlab = "Urban cover (%)", line = line_labs, cex.lab = xlab.cex)
  title(ylab = "Tricyclic (ng/L)", line = line_labs, cex.lab = ylab.cex)
  
  polygon(y = c(Tricyclic_model$estimates_second$lwr, Tricyclic_model$estimates_second$upr[101:1]),
          x = c(0:100,100:0), col = "grey90", border = FALSE)
  abline(h = LQ$Tricyclic, lty = 2, col = "brown")
  axis(1, tick = TRUE, line = 0, labels = FALSE,  tck = tck); axis(1, tick = FALSE, cex.axis = axis.cex, line = line_axis, gap.axis = -10)
  axis(2, tick = TRUE, line = 0, labels = FALSE,  tck = tck); axis(2, tick = FALSE, cex.axis = axis.cex, line = line_axis, gap.axis = -10)
  lines(c(0:100), Tricyclic_model$estimates_best$fit, lty = 1, lwd  = line_lwd)
  points(x = data_farmacos_by_class$urb, y = data_farmacos_by_class$Tricyclic, pch = 16, cex = cex.points)
  box()
  margins <- par()$mar
  par(new = TRUE, mar = c(0,0,0,0))
  plot(NA , type = "n", xaxt = "n", yaxt = "n", xlab = "", ylab = "", bty = "n", xlim = c(0,100), ylim = c(0,100))
  text(x = x_letter, y = y_letter, labels = letter, font = 2, cex = 1.5, adj = 0)
  par(mar = margins)
}


par(mfrow = c(3,2), mar = c(2.5,3.5,1.2,0.25))

all_plot(letter = "A)")
SSRI_plot(letter = "B)")
SNRI_plot(letter = "C)")
Aminoketone_plot(letter = "D)")
Tricyclic_plot(letter = "E)")


```


```{r, eval = FALSE, echo=FALSE, include=FALSE, fig.asp=1, fig.width=10, fig.align= "center"}

pdf("Resultados/Resultados Antidepressivos/Figuras/PDF/Antidepressivos_GAM_by_class_SEM_ZERO.pdf", width = 4, height = 3, pointsize = 9)
par(mfrow = c(3,2), mar = c(2.5,3.5,1.2,0.25))

all_plot(letter = "A)")
SSRI_plot(letter = "B)")
SNRI_plot(letter = "C)")
Aminoketone_plot(letter = "D)")
Tricyclic_plot(letter = "E)")


dev.off()

```



```{r, eval = FALSE, echo=FALSE, include=FALSE, fig.asp=0.5, fig.width=10, fig.align= "center"}

model_tabs_by_class <- list(SNRI_model$AICTAB,
  SSRI_model$AICTAB,
  Aminoketone_model$AICTAB,
  Tricyclic_model$AICTAB)

names(model_tabs_by_class) <- c("SNRI",
                       "SSRI",
                       "Aminoketone",
                       "Tricyclic")



order <- c("gam_0","gam_1","gam_2","gam_3","gam_4")

for(i in 1:length(model_tabs_by_class)){
  model_tabs_by_class[[i]] <- model_tabs_by_class[[i]][match(order,rownames(model_tabs_by_class[[i]])),]
}


write.csv(model_tabs_by_class,"Resultados/model_selection_GAM_concentrations_by_class.csv")
```

