---
title: "EMS"
author: "Rodolfo Pelinson"
date: "2024-11-14"
output: github_document
editor_options: 
  chunk_output_type: console
---


```{r,  echo= FALSE, eval = TRUE, warning=FALSE, message=FALSE, include=FALSE}

library(vegan)
library(shape)
library(scales)
library(metacom)

data_farmacos <- read.csv("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/data/antidepressivos_r.csv")
data_farmacos <- data_farmacos[,which(colnames(data_farmacos)!="Norfluoxetina")]
data_general <- read.csv("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/data/planilha_master_r.csv")

data_farmacos_reference <- data_farmacos[1,]
data_farmacos_class <- data_farmacos[2,]
data_farmacos <- data_farmacos[-c(1,2),]

data_farmacos$urb <- data_general$urb[match(data_farmacos$bacia,data_general$microbacia)]

data.frame(data_farmacos$bacia, data_farmacos$urb, data_farmacos$Decil)

data_farmacos$urb[data_farmacos$bacia == "ebb008" | 
                    data_farmacos$bacia == "ebb009" |
                    data_farmacos$bacia == "ebb011" |
                    data_farmacos$bacia == "ebb012"] <- 0 


data_farmacos$bacia[is.na(data_farmacos$urb)]

data_farmacos$urb[is.na(data_farmacos$urb)] <- data_farmacos$Decil[is.na(data_farmacos$urb)] + 5

urb <- data_farmacos$urb
Decil <- data_farmacos$Decil
bacia <- data_farmacos$bacia

data_farmacos <- data_farmacos[,-c(1,2,ncol(data_farmacos))]
data_farmacos_reference <- data_farmacos_reference[,-c(1,2)]
data_farmacos_class <- data_farmacos_class[,-c(1,2)]

data_farmacos <- data.frame(lapply(data_farmacos,as.numeric))

data_farmacos_reference <- data_farmacos_reference[,colSums(data_farmacos)>0]
data_farmacos_class <- data_farmacos_class[,colSums(data_farmacos) > 0]
data_farmacos <- data_farmacos[,colSums(data_farmacos) > 0]

data_farmacos_class <- unlist(c(data_farmacos_class))


data_farmacos_pa <- decostand(data_farmacos, method = "pa")

data_farmacos_pa_no_zero <- data_farmacos_pa[rowSums(data_farmacos_pa) > 0,]
data_farmacos_pa_zero <- data_farmacos_pa[rowSums(data_farmacos_pa) == 0,]

urb_no_zero <- urb[rowSums(data_farmacos_pa) > 0]
urb_zero <- urb[rowSums(data_farmacos_pa) == 0]

bacia_no_zero <- bacia[rowSums(data_farmacos_pa) > 0]
bacia_zero <- bacia[rowSums(data_farmacos_pa) == 0]


######################################################################
rownames(data_farmacos_pa_zero) <- bacia_zero
rownames(data_farmacos_pa_no_zero) <- bacia_no_zero

names(urb_no_zero) <- bacia_no_zero
names(urb_zero) <- bacia_zero




###PAREI AQUI!!!!



set.seed(2); order <- sample(1:nrow(data_farmacos_pa_zero))
reordered_data_farmacos_pa_zero <- data_farmacos_pa_zero[order,]
reordered_urb_zero<- urb_zero[order]



reordered_no_zero <- OrderMatrix(data_farmacos_pa_no_zero)
order_urb_no_zero <- match(rownames(reordered_no_zero),names(urb_no_zero))
reordered_urb_no_zero <- urb_no_zero[order_urb_no_zero]

reordered_data_farmacos_pa_zero <- reordered_data_farmacos_pa_zero[,match(colnames(reordered_no_zero), colnames(reordered_data_farmacos_pa_zero))]

data_farmacos_pa_plot <- rbind(reordered_data_farmacos_pa_zero, reordered_no_zero)

#urb_plot <- c(reordered_urb_no_zero[order(1:length(reordered_urb_no_zero), decreasing  = TRUE)], reordered_urb_zero[order(1:length(reordered_urb_zero), decreasing  = TRUE)]) 
#Aqui tem que inverter a ordem com relação à matriz, não lembro bem pq. Quando a função mesmo que reordena funciona, mas como ela nao está reordenando, precisa fazer manualmente

urb_plot <- c(reordered_urb_zero, reordered_urb_no_zero)

urb_plot_reverse <- urb_plot[length(urb_plot):1]

empty_com <- rep(0, nrow(data_farmacos_pa_plot))
riqueza <- rowSums(data_farmacos_pa_plot)
empty_com[riqueza == 0] <- 1

data_farmacos_pa_plot <- data.frame(data_farmacos_pa_plot, None_detected = empty_com)

farmacos_plus_empty <-  sub("_", " ",colnames(data_farmacos_pa_plot)) 

data.frame(names(urb_plot), rownames(data_farmacos_pa_plot))


```

To plot the matrix I used a custom function called "My_Imagine".

```{r}
source("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/scripts/functions/My_Imagine_function.R")

```


The matrix including sites where no antidepressant was detected.
```{r, message=FALSE, warning=FALSE, fig.width=10, fig.align="center", fig.asp=1, dev.args=list(pointsize = 15)}
My_Imagine(data_farmacos_pa_plot, col = c(0,1, "grey60"), top_margin = 7, left_margin = 3, bottom_margin = 0.1, fill = FALSE,
           Env1 = urb_plot_reverse, Env.col_1 = c("white","black"), Env.label_1 = "Urban cover", order = FALSE, speciesnames = farmacos_plus_empty,
           cex.site = 0.6, cex.species = 0.7, xline = -0.5, yline = -0.5, gap.axis = -10, Empty = ncol(data_farmacos_pa_plot), Empty_col = "lightblue3", speciesfont = 1)
```

The matrix excluding sites where no antidepressant was detected.
```{r, message=FALSE, warning=FALSE, fig.width=10, fig.align="center", fig.asp=1, dev.args=list(pointsize = 15)}

My_Imagine(data_farmacos_pa_no_zero, col = c(0,1, "black"), top_margin = 7, left_margin = 3, bottom_margin = 0.1, fill = FALSE, cex.site = 0.6, cex.species = 0.7, xline = -0.5, yline = -0.5, gap.axis = -10,
           Env1 = urb_no_zero, Env.col_1 = c("white","black"), Env.label_1 = "Urban cover", speciesnames = colnames(data_farmacos_pa_no_zero), speciesfont = 1, Empty = NULL)
```


```{r, eval = FALSE, echo=FALSE, include=FALSE, fig.asp=0.5, fig.width=10, fig.align= "center"}
pdf("Resultados/Resultados Antidepressivos/Figuras/PDF/EMS_empty.pdf", width = 6, height = 6)
My_Imagine(data_farmacos_pa_plot, col = c(0,1, "grey60"), top_margin = 7, left_margin = 3, bottom_margin = 0.1, fill = FALSE,
           Env1 = urb_plot_reverse, Env.col_1 = c("white","black"), Env.label_1 = "Urban cover", order = FALSE, speciesnames = farmacos_plus_empty,
           cex.site = 0.6, cex.species = 0.7, xline = -0.5, yline = -0.5, gap.axis = -10, Empty = ncol(data_farmacos_pa_plot), Empty_col = "lightblue3", speciesfont = 1)
dev.off()

pdf("Resultados/Resultados Antidepressivos/Figuras/PDF/EMS.pdf", width = 6, height = 6)
My_Imagine(data_farmacos_pa_no_zero, col = c(0,1, "black"), top_margin = 7, left_margin = 3, bottom_margin = 0.1, fill = FALSE, cex.site = 0.6, cex.species = 0.7, xline = -0.5, yline = -0.5, gap.axis = -10,
           Env1 = urb_no_zero, Env.col_1 = c("white","black"), Env.label_1 = "Urban cover", speciesnames = colnames(data_farmacos_pa_no_zero), speciesfont = 1)
dev.off()
```



Actual EMS analysis:
```{r}

coerencia <- data.frame(Coherence(data_farmacos_pa_no_zero, method = "r0", sims = 10000, orderNulls = TRUE, order = TRUE, seed = 1, scores = 1, allowEmpty = FALSE))
coerencia$stat <- round(coerencia$stat, 3)

turnover <- Turnover(data_farmacos_pa_no_zero, method = "r0", sims = 10000, fill = FALSE)
turnover$stat <- round(turnover$stat, 3)

bc <- BoundaryClump(data_farmacos_pa_no_zero)
bc$stat <- round(bc$stat, 3)

coerencia
turnover
bc
```
There is a nested pattern of antidepressant with clumped losses.

```{r, warning=FALSE}
scores <- OrderMatrix(data_farmacos_pa_no_zero, outputScores = T)$sitescores
cor.test(scores, urb_no_zero, method = "spearman")


scores2 <- OrderMatrix(data_farmacos_pa_no_zero, outputScores = T)$sitescores
scores2 <- scores2[order(scores2, decreasing = TRUE)]
scores_zero <- rep(scores2[1]*1.1, length(bacia_zero))
names(scores_zero) <- names(reordered_urb_zero)
scores2 <- c(scores_zero, scores2)
scores2 <- scores2[length(scores2):1]

cor.test(scores2, urb_plot, method = "spearman")
```


The gradient in antidepressant composition is associated with the urban cover gradient when we do not consider sites with no antidepressant detected. When we consider them, the association is highly significant.
