---
title: "Predictors of total concentration of antidepressants in streamwater (excluding
  observations)"
author: "Rodolfo Pelinson"
date: "2024-11-15"
output: github_document
editor_options: 
  chunk_output_type: console
---


Packages:
```{r, message=FALSE, warning=FALSE}
library(DHARMa)
library(AICcmodavg)
library(corrplot)
library(MuMIn)
library(vegan)
library(car)
library(lme4)
library(glmmTMB)
library(dplyr)
```

A few necessary functions to make the code more straightforward:
```{r, message = FALSE, warning=FALSE}
source("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/scripts/functions/plot_models_one_var.R")
source("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/scripts/functions/plot_models_two_var.R")
source("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/scripts/functions/confidence_interval.R")
source("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/scripts/ajeitando_planilhas.R")
```



#### Excluding observations from which there was more than 10% variation in urbanization from 2010 to 2021.

Excluding observations from which there was more than 10% variation in urbanization from 2010 to 2021.
```{r}
diff_watersheds_10_urb

new_predictors <- predictors
predictors_sem_10_urb <- predictors[-match(diff_watersheds_10_urb, rownames(new_predictors)),]
```




Performing the model selection procedure. Note that the name of the variables are in portuguese. 

Habitantes mean inhabitants
casas_sem_saneamento means houses without sanitation
renda means income.

First we make a matrix to check which pairs of variables are correlated (more than 50%) and therefore should not be together in the same model.
```{r, message = FALSE, warning=FALSE}

pred_mod_sel <- select(predictors_sem_10_urb,  casas_sem_saneamento, renda, habitantes)

#Standardizing response variables
Preditoras_stand <- decostand(pred_mod_sel, method = "stand")

smat <- abs(cor(Preditoras_stand)) <= .5
smat[!lower.tri(smat)] <- NA

colnames(smat) <- c(paste("cond(",colnames(smat)[1], ")", sep = ""),
                    paste("cond(",colnames(smat)[2], ")", sep = ""),
                    paste("cond(",colnames(smat)[3], ")", sep = ""))

rownames(smat) <- colnames(smat)

cor(Preditoras_stand)
smat
```

Now performing the model selection.
```{r}
all <- responses$all[-match(diff_watersheds_10_urb, rownames(responses))]

Preditoras_stand$all <- all

mod_global_all <- glmmTMB(all ~ 
                            #area +
                            casas_sem_saneamento +
                            habitantes +
                            renda + 
                            casas_sem_saneamento:renda+
                            #casas_sem_saneamento:renda:area+
                            habitantes:renda,
                            #habitantes:renda:area+
                            #casas_sem_saneamento:area+
                            #habitantes:area+
                            #renda:area,
                          data = Preditoras_stand, family = tweedie(link = "log"), na.action = "na.fail")


dredge_modelos_all <- MuMIn::dredge(mod_global_all, subset = smat)

models <- get.models(dredge_modelos_all, subset = delta < 2)

aictab(models)

dredge_modelos_all
```

Selected models include houses without sanitaiton in interaction with income OR just inhabitants OR inhabitants in interaction with income.




#### Excluding observations from which there was more than 5% variation in urbanization from 2010 to 2021.

Excluding observations from which there was more than 10% variation in urbanization from 2010 to 2021.
```{r}
diff_watersheds_5_urb

new_predictors <- predictors
predictors_sem_10_urb <- predictors[-match(diff_watersheds_5_urb, rownames(new_predictors)),]
```




Performing the model selection procedure. Note that the name of the variables are in portuguese. 

Habitantes mean inhabitants
casas_sem_saneamento means houses without sanitation
renda means income.

First we make a matrix to check which pairs of variables are correlated (more than 50%) and therefore should not be together in the same model.
```{r, message = FALSE, warning=FALSE}

pred_mod_sel <- select(predictors_sem_10_urb,  casas_sem_saneamento, renda, habitantes)

#Standardizing response variables
Preditoras_stand <- decostand(pred_mod_sel, method = "stand")

smat <- abs(cor(Preditoras_stand)) <= .5
smat[!lower.tri(smat)] <- NA

colnames(smat) <- c(paste("cond(",colnames(smat)[1], ")", sep = ""),
                    paste("cond(",colnames(smat)[2], ")", sep = ""),
                    paste("cond(",colnames(smat)[3], ")", sep = ""))

rownames(smat) <- colnames(smat)

cor(Preditoras_stand)
smat
```

Now performing the model selection.
```{r}
all <- responses$all[-match(diff_watersheds_5_urb, rownames(responses))]

Preditoras_stand$all <- all

mod_global_all <- glmmTMB(all ~ 
                            #area +
                            casas_sem_saneamento +
                            habitantes +
                            renda + 
                            casas_sem_saneamento:renda+
                            #casas_sem_saneamento:renda:area+
                            habitantes:renda,
                            #habitantes:renda:area+
                            #casas_sem_saneamento:area+
                            #habitantes:area+
                            #renda:area,
                          data = Preditoras_stand, family = tweedie(link = "log"), na.action = "na.fail")


dredge_modelos_all <- MuMIn::dredge(mod_global_all, subset = smat)

models <- get.models(dredge_modelos_all, subset = delta < 2)

aictab(models)

dredge_modelos_all
```

Selected models include just inhabitants OR inhabitants in interaction with income OR the model without effect of any predictors. The inclusion of the this last model probably happened because of the significant reduction in sample size (11 watersheds were removed).




#### Excluding observations from which there was more than 10% variation in subnormal constructions from 2010 to 2021.

Excluding observations from which there was more than 10% variation in urbanization from 2010 to 2021.
```{r}
diff_watersheds_10_AGSB

new_predictors <- predictors
predictors_sem_10_urb <- predictors[-match(diff_watersheds_10_AGSB, rownames(new_predictors)),]
```




Performing the model selection procedure. Note that the name of the variables are in portuguese. 

Habitantes mean inhabitants
casas_sem_saneamento means houses without sanitation
renda means income.

First we make a matrix to check which pairs of variables are correlated (more than 50%) and therefore should not be together in the same model.
```{r, message = FALSE, warning=FALSE}

pred_mod_sel <- select(predictors_sem_10_urb,  casas_sem_saneamento, renda, habitantes)

#Standardizing response variables
Preditoras_stand <- decostand(pred_mod_sel, method = "stand")

smat <- abs(cor(Preditoras_stand)) <= .5
smat[!lower.tri(smat)] <- NA

colnames(smat) <- c(paste("cond(",colnames(smat)[1], ")", sep = ""),
                    paste("cond(",colnames(smat)[2], ")", sep = ""),
                    paste("cond(",colnames(smat)[3], ")", sep = ""))

rownames(smat) <- colnames(smat)

cor(Preditoras_stand)
smat
```

Now performing the model selection.
```{r}
all <- responses$all[-match(diff_watersheds_10_AGSB, rownames(responses))]

Preditoras_stand$all <- all

mod_global_all <- glmmTMB(all ~ 
                            #area +
                            casas_sem_saneamento +
                            habitantes +
                            renda + 
                            casas_sem_saneamento:renda+
                            #casas_sem_saneamento:renda:area+
                            habitantes:renda,
                            #habitantes:renda:area+
                            #casas_sem_saneamento:area+
                            #habitantes:area+
                            #renda:area,
                          data = Preditoras_stand, family = tweedie(link = "log"), na.action = "na.fail")


dredge_modelos_all <- MuMIn::dredge(mod_global_all, subset = smat)

models <- get.models(dredge_modelos_all, subset = delta < 2)

aictab(models)

dredge_modelos_all
```

Selected models include just inhabitants OR houses without sanitation in interaction with income OR the model without effect of any predictors. The inclusion of the this last model probably happened because of the significant reduction in sample size (9 watersheds were removed).






#### Excluding observations from which there was more than 5% variation in subnormal constructions from 2010 to 2021.

Excluding observations from which there was more than 10% variation in urbanization from 2010 to 2021.
```{r}
diff_watersheds_5_AGSB

new_predictors <- predictors
predictors_sem_10_urb <- predictors[-match(diff_watersheds_5_AGSB, rownames(new_predictors)),]
```




Performing the model selection procedure. Note that the name of the variables are in portuguese. 

Habitantes mean inhabitants
casas_sem_saneamento means houses without sanitation
renda means income.

First we make a matrix to check which pairs of variables are correlated (more than 50%) and therefore should not be together in the same model.
```{r, message = FALSE, warning=FALSE}

pred_mod_sel <- select(predictors_sem_10_urb,  casas_sem_saneamento, renda, habitantes)

#Standardizing response variables
Preditoras_stand <- decostand(pred_mod_sel, method = "stand")

smat <- abs(cor(Preditoras_stand)) <= .5
smat[!lower.tri(smat)] <- NA

colnames(smat) <- c(paste("cond(",colnames(smat)[1], ")", sep = ""),
                    paste("cond(",colnames(smat)[2], ")", sep = ""),
                    paste("cond(",colnames(smat)[3], ")", sep = ""))

rownames(smat) <- colnames(smat)

cor(Preditoras_stand)
smat
```

Now performing the model selection.
```{r}
all <- responses$all[-match(diff_watersheds_5_AGSB, rownames(responses))]

Preditoras_stand$all <- all

mod_global_all <- glmmTMB(all ~ 
                            #area +
                            casas_sem_saneamento +
                            habitantes +
                            renda + 
                            casas_sem_saneamento:renda+
                            #casas_sem_saneamento:renda:area+
                            habitantes:renda,
                            #habitantes:renda:area+
                            #casas_sem_saneamento:area+
                            #habitantes:area+
                            #renda:area,
                          data = Preditoras_stand, family = tweedie(link = "log"), na.action = "na.fail")


dredge_modelos_all <- MuMIn::dredge(mod_global_all, subset = smat)

models <- get.models(dredge_modelos_all, subset = delta < 2)

aictab(models)

dredge_modelos_all
```

Selected models include just inhabitants OR inhabitants in interaction with income OR the model without effect of any predictors. The inclusion of the this last model probably happened because of the significant reduction in sample size (14 watersheds were removed).

