---
title: "Predictors of total concentration of SSRI antidepressants in streamwater"
author: "Rodolfo Pelinson"
date: "2024-11-15"
output: github_document
editor_options: 
  chunk_output_type: console
---

Packages:
```{r, message=FALSE, warning=FALSE}
library(DHARMa)
library(AICcmodavg)
library(corrplot)
library(MuMIn)
library(vegan)
library(car)
library(lme4)
library(glmmTMB)
library(dplyr)
```

A few necessary functions to make the code more straightforward:
```{r, message = FALSE, warning=FALSE}
source("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/scripts/functions/plot_models_one_var.R")
source("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/scripts/functions/plot_models_two_var.R")
source("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/scripts/functions/confidence_interval.R")
```



Performing the model selection procedure. Note that the name of the variables are in portuguese. 

Habitantes mean inhabitants
casas_sem_saneamento means houses without sanitation
renda means income.

First we make a matrix to check which pairs of variables are correlated (more than 50%) and therefore should not be together in the same model.
```{r, message = FALSE, warning=FALSE}
source("C:/Users/rodol/OneDrive/repos/Antidepressants_sp/scripts/ajeitando_planilhas.R")

pred_mod_sel <- select(predictors,  casas_sem_saneamento, renda, habitantes)

#Standardizing response variables
Preditoras_stand <- decostand(pred_mod_sel, method = "stand")

smat <- abs(cor(Preditoras_stand)) <= .5
smat[!lower.tri(smat)] <- NA

colnames(smat) <- c(paste("cond(",colnames(smat)[1], ")", sep = ""),
                    paste("cond(",colnames(smat)[2], ")", sep = ""),
                    paste("cond(",colnames(smat)[3], ")", sep = ""))

rownames(smat) <- colnames(smat)

cor(Preditoras_stand)
smat
```

Now performing the model selection.
```{r}
Preditoras_stand$SSRI <- responses$SSRI

mod_global_SSRI <- glmmTMB(SSRI ~ 
                            #area +
                            casas_sem_saneamento +
                            habitantes +
                            renda + 
                            casas_sem_saneamento:renda+
                            #casas_sem_saneamento:renda:area+
                            habitantes:renda,
                            #habitantes:renda:area+
                            #casas_sem_saneamento:area+
                            #habitantes:area+
                            #renda:area,
                          data = Preditoras_stand, family = tweedie(link = "log"), na.action = "na.fail")


dredge_modelos_SSRI <- MuMIn::dredge(mod_global_SSRI, subset = smat)

models <- get.models(dredge_modelos_SSRI, subset = delta < 2)

aictab(models)

dredge_modelos_SSRI
```

Selected models include only inhabitants as predictor.


```{r, eval = FALSE, echo = FALSE, include = FALSE}
write.table(data.frame(as.matrix(dredge_modelos_SSRI)), "Resultados/model_selection_SSRI.csv", sep = ",")
```


Plotting the best models:

```{r, fig.align='center', fig.asp=0.9, fig.width=6, dev.args=list(pointsize = 12)}
best_model <- models[[1]]

par(mar = c(3.5,5,1,0.1))
plot_models_one_var(best_model, var1 = pred_mod_sel$habitantes, xlab = "Number of inhabitants")
```

```{r, eval = FALSE, echo = FALSE, include = FALSE}
pdf(paste(caminho, "SSRI_Antidepressivos_vs_saneamento.pdf", sep = ""), width = 4, height = 3.5, pointsize = 7)
plot_models_one_var(best_model, var1 = pred_mod_sel$habitantes, xlab = "Number of inhabitants")
dev.off()
```

